\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-26 paper/subdocuments/results.Rnw

density1 <- density(log(bd.2003.ind$inc))
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "log(taxable income)", ylab = "density",
     axes = FALSE,
     xlim = c(-8, 10),
     ylim=c(0,0.5655167))
title(main="2003 vs 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(0,0),y=c(0.5655167,0.5655167))
legend(fig1legend,lty=1:2,cex=0.5, bty="n",
       legend=c("2003","2010"))
density2 <- density(log(bd.2010.ind$inc))
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
g10 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of 2003 Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

par(mfrow=c(1,3))
a<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,5.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 1993/94"))
abline(h=1,lty=2)
b<-reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
c<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,5.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<with_without_zeros,warning=FALSE>>=
dflong <- melt(df[,c("G_steink","G_steink0","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without zeros","including zeros")
ggplot(dflong[dflong$kanton=="CH" & dflong$steuerperiode>=1995.5,], aes(x=steuerperiode,y=Gini,shape=Type,linetype=Type))+geom_line(size=1)+theme_bw()+xlab("tax period")+theme(legend.justification=c(0,1),legend.position=c(0, 1))
ggplot(dflong[dflong$steuerperiode>=1995.5,], aes(x=steuerperiode,y=Gini,shape=Type,linetype=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")+theme(axis.text.x = element_text(angle = 60, hjust = 1))+theme(legend.justification=c(1,0),legend.position=c(1, 0))
@

@@

#####################################################
#         ACHTUNG: Bisher ohne Gewichte!            #
#####################################################
try(habe0911<-read.table("C:/Users/Hackstutz/Dropbox/Ungleichheit/HABE/HABE091011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
try(habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10<-data.frame(habe10$VerfuegbaresEinkommen08)
names(habe10)<-"inc_habe"
habe10$inc_habe[habe10$inc_habe<0]<-0 # One values is -20'000
habe10$inc_habe<-habe10$inc_habe*12/1000 # transform from monthly income to income per year

>>>>

density1 <- density(log(bd.2003.ind$inc))
plot(x = (density1$x), y = density1$y, type = "l",
     xlab = "log(taxable income)", ylab = "density",
     axes = FALSE,
     xlim = c(-8, 10),
     ylim=c(0,0.5655167))
title(main="2003 vs 2010",cex=0.6)
axis(side = 1)
axis(side = 2)
fig1legend <- list(x=c(0,0),y=c(0.5655167,0.5655167))
legend(fig1legend,lty=1:2,cex=1, bty="n",
       legend=c("2003","2010"))
density2 <- density(log(bd.2010.ind$inc))
lines(x = (density2$x), y = density2$y, type = "l",lty=2)

@@

par(mfrow=c(1,3))
g10 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,2),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of 2003 Distribution")
title(main=paste("Overall realtive density"))
abline(h=1,lty=2)
g1A <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,2), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
gA0 <- reldist(y=bd.2010.ind$inc, yo=bd.2003.ind$inc,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,2), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of 2003 Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))

# Polarization index

bd.2010.ind$wgt<-1
bd.2003.ind$wgt<-1

format(rpy(y=bd.2010.ind$inc,yo=bd.2003.ind$inc,
           ywgt=bd.2010.ind$wgt,yowgt=bd.2003.ind$wgt,pvalue=FALSE),
       digits=3) # Median Index, middle value is the estimate 
format(rpluy(y=bd.2010.ind$inc,yo=bd.2003.ind$inc,
             ywgt=bd.2010.ind$wgt,yowgt=bd.2003.ind$wgt,pvalue=FALSE),
       digits=3) # Lower Index
format(rpluy(y=bd.2010.ind$inc,yo=bd.2003.ind$inc,
             ywgt=bd.2010.ind$wgt,yowgt=bd.2003.ind$wgt,pvalue=TRUE,
             upper=TRUE),
       digits=3) # Upper index

@

@@

par(mfrow=c(1,3))
a<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               ylim=c(0.5,2.0),
               bar=TRUE, quiet=FALSE,
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Overall relative density 1993/94"))
abline(h=1,lty=2)
b<-reldist(y=pooled_i, yo=normal_i,
               show="effect",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,2.0), ylab="",
               smooth=0.4, ci=FALSE,
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of Median shift"))
abline(h=1,lty=2)
c<-reldist(y=pooled_i, yo=normal_i,
               smooth=0.4, ci=FALSE,
               show="residual",
               bar=TRUE, quiet=FALSE,
               ylim=c(0.5,2.0), ylab="",
               yolabs=seq(-1,3,by=0.5),
               xlab="Proportion of Normal-Case-Distribution")
title(main=paste("Effect of different shape"))
abline(h=1,lty=2)
par(mfrow=c(1,1))
@

@@

<<with_without_zeros,warning=FALSE>>=
dflong <- melt(df[,c("G_steink","G_steink0","kanton","steuerperiode")], id=c("kanton","steuerperiode"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without zeros","including zeros")
ggplot(dflong[dflong$kanton=="CH" & dflong$steuerperiode>=1995.5,], 
       aes(x=steuerperiode,y=Gini,shape=Type,linetype=Type))+
  scale_y_continuous(limits=c(0.18,0.6))+
  scale_x_continuous(limits=c(1994,2012),breaks=number_ticks(10)) +
  geom_line(size=0.5)+
  geom_point(aes(shape=Type),size=3)+
  theme_bw()+
  xlab("tax period")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))
#ggplot(dflong[dflong$steuerperiode>=1995.5,], aes(x=steuerperiode,y=Gini,shape=Type,linetype=Type))+geom_line()+facet_wrap(~kanton)+theme_bw()+xlab("tax period")+theme(axis.text.x = element_text(angle = 60, hjust = 1))+theme(legend.justification=c(1,0),legend.position=c(1, 0))
@

@@

#####################################################
#         ACHTUNG: Bisher ohne Gewichte!            #
#####################################################
try(habe0911<-read.table("C:/Users/Hackstutz/Dropbox/Ungleichheit/HABE/HABE091011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
try(habe0911<-read.table("P:/WGS/FBS/ISS/Projekte laufend/SNF Ungleichheit/Datengrundlagen/HABE/2009 bis 2011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
try(habe0911<-read.table("C:/Users/rudi/Dropbox/Ungleichheit/HABE/HABE091011/HABE091011_Standard_130717UOe.txt", header=TRUE),silent=TRUE)
g2009 <- read.csv("C:/Users/rudi/Dropbox/Ungleichheit/HABE/HABE091011/HABE2009_Gewichte_140625UOe.txt",sep="\t")
g2010 <- read.csv("C:/Users/rudi/Dropbox/Ungleichheit/HABE/HABE091011/HABE2010_Gewichte_140625UOe.txt",sep="\t")
g2011 <- read.csv("C:/Users/rudi/Dropbox/Ungleichheit/HABE/HABE091011/HABE2011_Gewichte_140625UOe.txt",sep="\t")
names(g2009)[3:4]<-c("SRH","Gewicht")
names(g2010)[3:4]<-c("SRH","Gewicht")
names(g2011)[3:4]<-c("SRH","Gewicht")
jg091011 <- rbind(g2009,g2010,g2011)
all.equal(match(jg091011$HaushaltID,habe0911$HaushaltID),1:nrow(habe0911))
habe0911$jahresgewicht <- jg091011

habe10<-habe0911 %.% 
  filter(Jahr08==2010)
habe10<-data.frame(habe10$VerfuegbaresEinkommen08)
names(habe10)<-"inc_habe"
habe10$inc_habe[habe10$inc_habe<0]<-0 # One values is -20'000
habe10$inc_habe<-habe10$inc_habe*12/1000 # transform from monthly income to income per year
